---
title: "BayesianInference"
author: "Ashwani Rao"
date: "July 12, 2015"
output: pdf_document
---

Purpose is to play with Bayesian Inference mechanism with flip of coins.

Following is R code to generate sequence of flip of coins with a biased coin.
```{r}
flip_coins <- function(n, bias) {
  nums <- runif(n)
  sapply(nums, function(val) if (val > bias) FALSE else TRUE)
}
flip_coins(10, 0.5) # Flip 10 coins with a fair coin
flip_coins(10, 0.3) # Flip 10 coins with probability of head 0.3

```
lik<- function(bias, flips) {
  total_head <- sum(flips) 
  total_obv <- length(flips)
  n_choose_k <- choose(total_obv, total_head)
  n_choose_k * (bias ^ total_head) * ((1 - bias) ^ (total_obv - total_head))
}


# posterior function
post <- function(likelihood, priors) {
  likelihood * priors
}
# normalized posterior function
  post_normalize <- function(flips, hypothesis_space) {
    likelihoods <- sapply(hypothesis_space$hypothesis, lik, flips=flips)
    posteriors <- likelihoods * hypothesis_space$priors
    sum_posterior <- sum(posteriors)
    posteriors / sum_posterior
}
```{r}
library(ggplot2)
ggplot(df, aes(x=x, y=y)) + geom_point(size=2)
```


We will generate data likelihood at various hypothesis of flip probability. We will plot these likelihoods to find at what hypothesis the max out.
```{r}
# following function will generate  a dataframe with three columns. Firt column is the actualy bias of the coin used to flip 10 times.
# Second columns is our hypothesis probability of the bias
# Third Columns is the likelihood of the data based on the hypothesis probability
gen_lik <- function() {
  flip_prob <- NULL
  hypo_prob <- NULL
  likelihood <- NULL
  for(flip_bias in seq(0,1, by=0.1)) {
    flips <- flip_coins(10, flip_bias)
    for (prob in hypo_space$hypothesis) {
      flip_prob <- c(flip_prob, as.character(flip_bias))
      hypo_prob <- c(hypo_prob, prob)
      likelihood <- c(likelihood, lik(prob, flips))
    }
  }
  data_frame <- data.frame(flip_prob=flip_prob, hypo_prob=hypo_prob, likelihood=likelihood)
  data_frame
}
# This function plot likelihood of data for each of the hypothesis probability
# for 10 flips of coins (flipped according to flip prob for that experiment).
# In the plot likelhood should max when coin flipped probability is equal to hypothesis probability
plot_likelihoods<- function() {
  df <- gen_lik()
  # select a subset of data
  selected_probs <- sample(df$flip_prob, 5)
  df <- df[df$flip_prob %in% selected_probs, ]
  p <- ggplot(data=df, aes(x=hypo_prob, y=likelihood, colour=flip_prob)) + geom_point(shape=1) + facet_grid(. ~ flip_prob)
  p
}
```
